Draft information

### 2019-04-26 paper/draft-info.Rmd
Format draft info

---
title: "The pollination trade-off"
subtitle: "Draft information"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}

@@

## Specific requests to coauthors

@@

## Changes

>>>>

---
title: "Draft information"
subtitle: "version: draft-4.0"
date: "2019-04-26"
# author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
# classoption: twocolumn
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}

@@

## Requests to coauthors

@@

## Changes since last draft
